Telemetry Module for Solar Vehicle

### 2021-06-17 documentation/FinalPaper/paper.tex

@@

% threads 
\subsection{Support Vehicle Unit}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SVU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SVU.}
    \label{fig:SCU_circuit}
\end{figure}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI

>>>>

The system thread and the CAN receiver thread having the lowest priority always run when no other high priority thread wants to execute. In the system thread, messages are received via RF, decoded and the action connected to the message is executed. This includes for instance injecting a message on the CAN bus. The CAN receiver thread tries to receive new messages from the CAN bus. These messages then need to be passed to the two high priority threads, which process them.

This inter-thread communication is performe

@@

% threads 
\subsection{Support Vehicle Unit}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{documentation/images/SVU_CircuitDiagram.pdf}
    \caption{The circuit diagram for the SVU.}
    \label{fig:SVU_circuit}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[height=4.5cm]{documentation/images/SVU_threads.pdf}
    \caption{The execution flow of the 2 threads running in the SVU.}
    \label{fig:SVU_threads}
\end{figure}
% threads
\subsection{\todo{Graphical User Interface}}
% GUI
